Maintenance planning on French military aircraft operations

### 2017-12-19 latex/ROADEF2018/article_roadef_2018_alt.tex
changed name of ROADEF dir

% Le titre court
\def\shorttitle{Titre court}

@@

\institute{
Institut Supérieur de l'Aéronautique et de l'Espace \\
\email{\{franco.peschiera,alain.hait,olga.battaia,nicolas.dupin\}@isae-supaero.fr}
}

@@

\section{Introduction}
    The Military Flight and Maintenance Planning is a problem consisting on the assignment of missions and maintenance tasks to military aircraft. It is a variant of the Flight and Maintenance Planning problem where flights are not modeled geographically but they are assumed to include a round-trip to the base. It also includes different objectives and constraints. Although the former has been studied in literature in \cite{Cho2011,Chastellux2017,Kozanidis2008}, it has not received as much attention as the latter.

@@

    The problem consists in the planning of the maintenance operations for military aircraft and the assignment of these aircraft to already scheduled missions. In order to generalize the formulation, from now on aircraft will be named "resources" and missions will be named "tasks". A series of $v \in \mathcal{V}$ tasks are planned along a horizon divided into $t \in \mathcal{T}$ periods. Each task requires a certain number $rr_{v}$ of resources $a \in \mathcal{A}$ which it employs for a time duration defined by $rh_{v}$ in each period. Set $cd_{v} \subset \mathcal{A}$ lists the resources that can be assigned to each task.

    % The assignment of a resource to a task is not decided for the whole duration of the task. After a minimum amount of time ($minTIME_v$), a resource can be freed and exchanged for another one, even if the task it is assigned to has not finished. The total number of resources being used at any given time in a specific task can never be less than the required $REQ_{vt}$.

    % \subsection{Resources}
    % \label{def:resource}

    Resources require recurrent preventive maintenance operations. The frequency of maintenance operations is defined by 2 factors: the amount of time $me$ elapsed since the last maintenance operation and the amount of time $mu$ for which the resource has been used since the last maintenance operation. The following states $s \in \mathcal{S}$ are possible for a resource: assigned to a task ('V'), receiving maintenance ('M'), available ('A'), needing maintenance ('N'). A maintenance operation takes an amount of time equal to $md$ periods and cannot be interrupted. The number of resources under maintenance in any period is restricted by its capacity $c_t$. In the following we present a new mathematical model for this problem. Unlike previous work, it assigns aircraft to missions, instead of just using an aggregate demand. 
    % We will call "remaining elapsed time" (or $ret$) to the amount of time that needs to pass in order for the resource to need a maintenance at any given period.

@@

    % \paragraph{Resource's states}
    % \label{def:res-state}

@@

    % \subsection{Decisions}

    % \subsection{Parameters}

    % \begin{tabular}{p{10mm}lp{110mm}}
    % $c_t$            & : & number of resources that can be in maintenance in period $t$. \\
    % $cd_v$           & : & resources that satisfy task's $v$ needs. \\
    % $rh_{vt}$        & : & time consumed of any resource when assigned to task $v$ in period $t$. \\
    % $rr_{vt}$        & : & number or resources to assign to task $v$ in period $t$. \\            
    % $mu$             & : & maximum used time for each resource between maintenances. \\    
    % $me$             & : & maximum elapsed time for each resource between maintenances. \\    
    % $md$             & : & maintenance duration, in periods. \\        
    % $rut\_i_a$       & : & remaining used time for resource $a$ at the beginning of horizon. \\        
    % $ret\_i_a$       & : & remaining elapsed time for resource $a$ at the beginning of horizon. \\
    % $state\_i_{at}$  & : & some $s \in \mathcal{S}$ in case the resource $a$ has a fixed state. \\
    % \end{tabular}
    % \bigskip

    % \subsection{Variables}

    The decision variables manage the previously defined resources. We can summarize the main decisions the following way: if resource $a$ is in state $s$ in each period $t$ and if resource $a$ is assigned to task $v$ in period $t$.

    \begin{tabular}{p{15mm}lp{105mm}}
        $task_{avt}$        & : & 1 if resource $a \in cd_v$ is assigned to task $v$ in period $t$, 0 otherwise. \\  
        $state_{ast}$       & : & 1 if resource $a$ is in state $s$ in period $t$, 0 otherwise. \\  
        $start_{at}$        & : & 1 if resource $a$ starts maintenance in period $t$, 0 otherwise. \\
        $ret_{at}$          & : & remaining elapsed time (integer) for resource $a$ after period $t$. \\  
        $rut_{at}$          & : & remaining usage time (integer) for resource $a$ after period $t$. \\  
        $used_{at}$         & : & time (integer) used by resource $a$ in period $t$. \\
        $min\_avail$        & : & min number (integer) of available resources in any period. \\
        $max\_maint$        & : & max number (integer) of resources in maintenance in any period. \\
    \end{tabular}
    \bigskip

    % \subsection{Constraints}

    The objective is to both minimize the maximum number of maintenances and maximize the minimal number of available aircraft:

    \begin{align}
        & \text{Min}\, (max\_maint) \\
        & \text{Max}\, (min\_avail)
    \end{align}

    Subject to:

    \begin{align}
        %%%%%%%%%%%%%%%%%%%
        % MAIN CONSTRAINTS
        %%%%%%%%%%%%%%%%%%%
        % maximum capacity:
        & \sum_{a \in \mathcal{A}} state_{ast} \leq c_{t}
                & t \in \mathcal{T}, s = \mq{M} \label{eq:capacity}\\
        % minimum resources
        & \sum_{a \in cd_v} task_{avt} \geq rr_{v}
                & t \in \mathcal{T}, v \in \mathcal{V},  \label{eq:taskres}\\
        % max one task per period
        & \sum_{v \in \mathcal{V}} task_{avt} \leq 1
                & t \in \mathcal{T}, a \in \mathcal{A} \label{eq:maxtasks}\\
        % if assigned to task: in working state
        & state_{ast} \geq task_{avt} 
                & \hspace{10mm} t \in \mathcal{T}, a \in cd_v, v \in \mathcal{V}, s = \mq{V} \label{eq:state1}\\
        % if no working state, no assigned to any task
        & state_{ast} + task_{avt} \leq 1
                & \hspace{10mm} t \in \mathcal{T}, a \in cd_v, v \in \mathcal{V}, s \neq \mq{V} \label{eq:state3}\\
        % only one state. If we take out the 'do nothing' state, this could be \leq
        & \sum_{s \in \mathcal{S}} state_{ast} = 1 
                & \hspace{10mm} t \in \mathcal{T}, a \in \mathcal{A} \label{eq:state2}
    \end{align}

    % These constraints are the the main constraints of the model.
    % The number of resources assigned to a single task and under maintenance 
    Tasks' resource requirements are defined by \ref{eq:taskres}, maintenance capacity is controlled by \ref{eq:capacity}. Constraints \ref{eq:state1} and \ref{eq:state3} tie states with the assignment to a task. Maximum tasks and states assigned to each resource is guaranteed by \ref{eq:maxtasks} and \ref{eq:state2}.

    \begin{align}
        %%%%%%%%%%%%%%%%%%%
        % BALANCES
        %%%%%%%%%%%%%%%%%%%
        % definition of consumed resource hours:
        & used_{at} \geq \sum_{v \in \mathcal{V}} task_{avt} \times rh_{v}
                & a \in \mathcal{A}, t \in \mathcal{T} \label{eq:usage}\\
        % remaining used time
        & rut_{at} \leq (rut_{at-1} - used_{at}) + (mu \times start_{at})
                & t \in \mathcal{T}, a \in \mathcal{A} \label{eq:balance1}\\
        % remaining elapsed time. TODO: improve this constraint like the maintenance state duration
        & ret_{at} \leq (ret_{at-1} - 1) + (me \times start_{at})
                & t \in \mathcal{T}, a \in \mathcal{A} \label{eq:balance2}
    \end{align}

@@

    The definition of the consumption of hours for each resource at each period is forced by \ref{eq:usage}. The monthly remaining usage and elapsed time are calculated by \ref{eq:balance1} and \ref{eq:balance2} respectively.
     % This is then applied in \ref{eq:balance1} to get the remaining usage time at each period for each resource. Similarly, the \ref{eq:balance2} calculates the remaining elapsed time at each period and resource.

    \begin{align}
        %%%%%%%%%%%%%%%%%%%
        % STATES
        %%%%%%%%%%%%%%%%%%%
        % if start maintenance, at least X periods
        & state_{ast_2} \geq start_{at_1} 
                & \hspace{10mm} (t_1, t_2) \in \mathcal{T}, t_1 \leq t_2 \leq t_1 + md - 1, a \in \mathcal{A}, s = \mq{M} \label{eq:start1}\\
        % if maintenance doesn't start, we cannot have maintenance:
        & \sum_{t_1 \in \mathcal{T}} start_{at_1} \geq state_{ast_2} 
                & \hspace{10mm} t_2 \in \mathcal{T}, t_1 \leq t_2 \leq t_1 + md - 1, a \in \mathcal{A}, s = \mq{M} \label{eq:start2}
    \end{align}

@@

    The coupling between the start of each maintenance and the maintenance state is done by \ref{eq:start1} and \ref{eq:start2}.
    % This way resources need to have started a maintenance to receive it and have to have maintenance for a minimum period after having starting it.

    \begin{align}
        %%%%%%%%%%%%%%%%%%%
        % OBJECTIVE
        %%%%%%%%%%%%%%%%%%%
        % min available
        & min\_avail \leq \sum_{a} state_{ast}
                & \hspace{10mm} t \in \mathcal{T}, a \in \mathcal{A}, s = \mq{A} \label{eq:available}\\
        % max maintenance
        & max\_maint \geq \sum_{a} state_{ast}
                & \hspace{10mm} t \in \mathcal{T}, a \in \mathcal{A}, s = \mq{M} \label{eq:maintenance}
    \end{align}

    % These constraints define the possible objectives.
    The definitions of the two previously defined objectives is done by \ref{eq:available} and \ref{eq:maintenance}.

@@

    % \begin{align}
    %     %%%%%%%%%%%%%%%%%%%
    %     % HORIZON
    %     %%%%%%%%%%%%%%%%%%%
    %     % TODO: initialize maintenance states too!
    %     % rut initialize
    %     & rut_{at} = rut\_ini_a
    %             & \hspace{10mm} t = 0, a \in \mathcal{A} \label{eq:remaining1}\\
    %     % ret initialize
    %     & ret_{at} = ret\_ini_a
    %             & \hspace{10mm} t = 0, a \in \mathcal{A} \label{eq:remaining2}\\
    %     % fixed states during planning period
    %     & state_{ast} = 1
    %             & \hspace{10mm} t \in \mathcal{T}, a \in \mathcal{A}; s \in \mathcal{S}\, | if\, state\_ini_{at} = s \label{eq:fixedstates}
    % \end{align}

@@

%\section{Conclusions}

 %   The present modelization is a new way to formulate the Military Flight Planning Model. Unlike previous work, it assigns aircraft to missions instead of just using an aggregate hourly demand per period. This is useful in order to improve the model by including minimum durations for mission assignment.

@@

\bibliographystyle{plain}
\selectlanguage{french}
\bibliography{MFMP}
% \begin{thebibliography}{2}
% \bibitem{toth02}
% Paolo Toth and Daniele Vigo.
% \newblock \emph{The Vehicle Routing Problem}.
% \newblock Monographs on Discrete Mathematics and Applications. Society for Industrial and Applied Mathematics, 2002.
% \bibitem{kirkpatrick83}
% Scott Kirkpatrick, C~Daniel Gelatt, and Mario~P Vecchi.
% \newblock Optimization by simmulated annealing.
% \newblock \emph{science}, 220\penalty0 (4598):\penalty0 671--680, 1983.

% \end{thebibliography}

>>>>

% Le titre court
% \def\shorttitle{Titre court}

@@

\institute{
ISAE-SUPAERO, Université de Toulouse, France \\
\email{\{franco.peschiera,alain.hait,olga.battaia,nicolas.dupin\}@isae-supaero.fr}
}

@@

\section{Introduction}
    The Military Flight and Maintenance Planning Problem considered here aims to assign missions and maintenance tasks to military aircraft. It is a variant of the Flight and Maintenance Planning problem where flights are not modelled geographically since a round-trip to the base is assumed for each flight. It also includes different objectives and constraints. Although the former has been studied in literature in \cite{Cho2011,Chastellux2017,Kozanidis2008,Verhoeff2015}, it has not received as much attention as the latter. In the following, the problem with already scheduled missions is considered.

@@

    The problem consists in assigning military aircraft to a given set of missions while scheduling the maintenance operations over a time horizon.
    In order to generalize the formulation, from now on aircraft will be named "resources" and missions will be named "tasks". A series of $j \in \mathcal{J}$ tasks are planned along a horizon divided into $t \in \mathcal{T}$ periods. Since all tasks are already scheduled, we know time periods $T_j \subset \mathcal{T}$ in which they will be realized. Similarly, all the tasks to be realized in period $t$ are known and defined by set $J_t \subset \mathcal{J}$. Each task requires a certain number $r_{j}$ of resources $i \in \mathcal{I}$ which it employs for a time duration defined by $h_j$ in each period. Set $a_{j} \subset \mathcal{I}$ lists the resources that can be assigned to each task and set $O_i \subset \mathcal{J}$ consists of tasks for which resource $i$ can be used. The number of resources in use for each period $d_t$ is also known.% (it is obtained by summing all $r_j$ for tasks $j \in J_t$).

    % The assignment of a resource to a task is not decided for the whole duration of the task. After a minimum amount of time ($minTIME_j$), a resource can be freed and exchanged for another one, even if the task it is assigned to has not finished. The total number of resources being used at any given time in a specific task can never be less than the required $REQ_{vt}$.

    % \subsection{iesources}
    % \label{def:resource}

    Resources require recurrent preventive maintenance operations since the realization of tasks diminish the remaining usage time of resources. A resource cannot be used for a task $j$ if its remaining usage time is less that usage $h_j$ required by task $j$. A maintenance operation assigns to the resource exactly $H$ units of remaining usage time. The remaining usage time not used before the maintenance operation is lost. %Independently of its usage, each resource has to be maintained each $t^u$ periods of time since the end of the last maintenance operation. 
		A maintenance operation takes exactly $m$ periods and cannot be interrupted: during this time the resource cannot be assigned to any task. Some resources can be in maintenance at the beginning of the planning horizon, $n_t$ is used for the number of aircraft in such planned maintenance per period $t$ and defined only for the first $m-1$ time periods. In the next section, we present a new mathematical model for this problem.
    % We will call "remaining elapsed time" (or $ret$) to the amount of time that needs to pass in order for the resource to need a maintenance at any given period.

@@

    % \paragraph{iesource's states}
    % \label{def:res-state}

@@

    The decision variables manage the previously defined resources.  %We can summarize the main decisions the following way: if resource $i$ starts maintenance in period $t$ and if resource $i$ is assigned to task $j$ in period $t$. We will call $\mathcal{T}_0$ to periods that include the period before the first, $0$, and $d_t$ the number of resources assigned to some task in period $t$. This parameter only should take some value in the first $md-1$ periods of the planning horizon.

    \begin{tabular}{p{5mm}lp{165mm}}
        $A_{jti}$           & =&1 if task $j \in J$ in period $t\in T_j$ is realized with resource $i \in a_j$, 0 otherwise. \\  
        % $state_{ist}$       & = & 1 if resource $i$ is in state $s$ in period $t$, 0 otherwise. \\  
        $M_{it}$            & =&1 if resource $i \in I$ starts maintenance in period $t \in \mathcal{T}$, 0 otherwise. \\
        $rut_{it}$          & =&remaining usage time (continuous) for resource $i \in I$ at the end of period $t \in \mathcal{T}$. \\  
        % $ret_{it}$          & = & remaining elapsed time (integer) for resource $i$ after period $t \in \mathcal{T}0$. \\  
        % $used_{it}$         & = & time (integer) used by resource $i$ in period $t$. \\
        $U_{max}$        & =&maximal number (integer) of unavailable resources in any period. \\
        $M_{max}$        & =&maximal number (integer) of resources in maintenance in any period. \\
    \end{tabular}
Note that  $A_{jti}$ and $M_{it}$ are initially set up to 0 for all resources already in maintenance at the beginning of the planning period for the remaining time periods of maintenance. The remaining usage time for each resource at the beginning of the planning period is used to initialize $rut_{i0}$. 
    % \subsection{Constraints}

    The objective is to simultaneously minimize the maximum number of maintenances and the maximum number of unavailable aircraft. 
 % The objective is to minimize the maximum number of unavailable aircraft at any time of the planning horizon:
    \begin{align}
        & \text{Min}\; w \times M_{max} + U_{max}
    \end{align}
    where relative weight $w$ is chosen by the decision maker. The following constraints are used.       
    \begin{align}
        %%%%%%%%%%%%%%%%%%%
        % MAIN CONSTRAINTS
        %%%%%%%%%%%%%%%%%%%
        % maximum capacity1:
        & \sum_{t' = 1}^{t} \,\, \sum_{i \in \mathcal{I}} M_{it'} + n_{t} \leq M_{max}
                & t =1, 2, ..., m-1 \label{eq:capacity1}\\
               % maximum capacity2:                
               & \sum_{t' = t - m+1}^{t} \,\, \sum_{i \in \mathcal{I}} M_{it'} \leq M_{max}
        & t =m, ..., |\mathcal{T}|  \label{eq:capacity2}\\
               %avail
               & \sum_{t' = 1}^{t} \,\, \sum_{i \in \mathcal{I}} M_{it'} + n_{t} + d_t\leq U_{max} 
                & t =1, 2, ..., m-1 \label{eq:avalaibility1}\\
               % maximum capacity2:                
               & \sum_{t' = t - m+1}^{t} \,\, \sum_{i \in \mathcal{I}} M_{it'} + d_t\leq U_{max} 
        & t =m, ..., |\mathcal{T}|  \label{eq:avalaibility2}\\
        % % maximum capacity:
        % & \sum_{t' = \max{\{1, t - m+1\}}}^{t} \,\, \sum_{i \in \mathcal{I}} M_{it'} + n_{t} \leq M_{max}
        %         & t \in \mathcal{T} \label{eq:capacity}\\
        % % maximum avaliability:
        % & \sum_{t' = \max{\{1, t - m+1\}}}^{t} \,\, \sum_{i \in \mathcal{I}} M_{it'} + d_{t} + n_{t} \leq U_{max}
        %         & \hspace{10mm} t \in \mathcal{T}  \label{eq:avalaibility}\\
        % or maintenance or task:
        % minimum resources
        & \sum_{i \in a_j} A_{jti} = r_{j}
                & j \in \mathcal{J}, t \in T_j  \label{eq:taskres}\\
			  & \sum_{t' = \max{\{1, t - m+1\}}}^{t} M_{it'} + \sum_{j \in J_t \cap O_i} A_{jti} \leq 1
                & t \in \mathcal{T}, i \in \mathcal{I} \label{eq:state}
    \end{align}
    % $$H*M_{it} - Heures de vol entre t_1 et t \leq H*(M_{it_1}+1) i \in I, t \geq t-1 \in T$$
    % $$t_1M_{it_1} \geq tM_{it} - D_{max} \foreach i \in I, t>t-1, t_1\geq D_{max}-D_i$$
    % These constraints are the the main constraints of the model.
    % The number of resources assigned to a single task and under maintenance 
    % Maintenance capacity is controlled by \ref{eq:capacity}. The number of unavailable resources is defined by \ref{eq:avalaibility}. Tasks' resource requirements are defined by \ref{eq:taskres}. Constraints \ref{eq:state} guarantee that a resource can be used only for one task or maintenance operation at the same period.  
    Maintenance capacity is controlled by (\ref{eq:capacity1})-(\ref{eq:capacity2}). The number of unavailable resources is defined by (\ref{eq:avalaibility1})-(\ref{eq:avalaibility2}). Tasks' resource requirements are defined by (\ref{eq:taskres}). Constraints (\ref{eq:state}) guarantee that a resource can be used only for one task or maintenance operation at the same period.  
    \begin{align}
        %%%%%%%%%%%%%%%%%%%
        % BALANCES
        %%%%%%%%%%%%%%%%%%%
        % definition of consumed resource hours:
        % & used_{it} \geq \sum_{j \in \mathcal{J}} A_{ijt} \times h_{j}
        %         & i \in \mathcal{I}, t \in \mathcal{T} \label{eq:usage}\\
        % definition of consumed resource hours (bigger):
        % & used_{it} \geq A_{ijt} \times h_{j}
        %         & i \in \mathcal{I}, t \in \mathcal{T}, j \in \mathcal{J} \label{eq:usage2}\\
        % remaining used time
         & rut_{it} \leq rut_{it-1} - \sum_{j \in J_t \cap O_i} A_{jti} \times h_{j} + H \times M_{it}
                & t \in \mathcal{T}, i \in \mathcal{I} \label{eq:balance1}\\
        % remaining elapsed time. TODO: improve this constraint like the maintenance state duration
        % & ret_{it} \leq (ret_{it-1} - 1) + (me \times M_{it})
        %         & t \in \mathcal{T}, i \in \mathcal{I} \label{eq:balance2}\\
        %& rut_{i0} = rut^{Init}_i
          %      & i \in \mathcal{I} \label{eq:initial}\\
        % & ret_{it} = retInit_r
        %         & t = 0, i \in \mathcal{I} \label{eq:initial2}\\
        % & ret_{it} \leq me
        %         & t \in \mathcal{T}, i \in \mathcal{I} \label{eq:me}\\
        & rut_{it} \geq H \times M_{it}
                & i \in \mathcal{I}, t \in \mathcal{T}\label{eq:balance2}\\	
				& rut_{it} \in [0,H]
                & i \in \mathcal{I}, t \in \mathcal{T} \label{eq:mu}
    \end{align}

@@

    The remaining usage time is defined by (\ref{eq:balance1}) and its limits by (\ref{eq:balance2})-(\ref{eq:mu}). 
     % This is then applied in \ref{eq:balance1} to get the remaining usage time at each period for each resource. Similarly, the \ref{eq:balance2} calculates the remaining elapsed time at each period and resource.

    % \begin{align}
        %%%%%%%%%%%%%%%%%%%
        % STATES
        %%%%%%%%%%%%%%%%%%%
        % if start maintenance, at least X periods
        % & state_{ist} \geq M_{it_1} 
        %         & \hspace{10mm} (t_1, t) \in \mathcal{T}, t_1 \leq t \leq t_1 + md - 1, i \in \mathcal{I}, s = \mq{M} \label{eq:start1}\\
        % % if maintenance doesn't start, we cannot have maintenance:
        % & \sum_{t_1 \in \mathcal{T}} M_{it_1} \geq state_{ist} 
        %         & \hspace{10mm} t \in \mathcal{T}, t_1 \leq t \leq t_1 + md - 1, i \in \mathcal{I}, s = \mq{M} \label{eq:start2}\\
        % availqbility definition:
        % & Umax \leq \sum_{i} state_{ist}
        %         & \hspace{10mm} t \in \mathcal{T}, i \in \mathcal{I}, s = \mq{A} \label{eq:available}
    % \end{align}

@@

    % The coupling between the start of each maintenance and the maintenance state is done by \ref{eq:start1} and \ref{eq:start2}. The definition of the previously mentioned objective is done by \ref{eq:available}.
    % This way resources need to have started a maintenance to receive it and have to have maintenance for a minimum period after having starting it.

    % \begin{align}
        %%%%%%%%%%%%%%%%%%%
        % OBJECTIVE
        %%%%%%%%%%%%%%%%%%%
        % min available
        % max maintenance
        % & Mmax \geq \sum_{i} state_{ist}
        %         & \hspace{10mm} t \in \mathcal{T}, i \in \mathcal{I}, s = \mq{M} \label{eq:maintenance}
    % \end{align}

    % These constraints define the possible objectives.

@@

    % \begin{align}
    %     %%%%%%%%%%%%%%%%%%%
    %     % HORIZON
    %     %%%%%%%%%%%%%%%%%%%
    %     % TODO: initialize maintenance states too!
    %     % rut initialize
    %     & rut_{it} = rut\_ini_a
    %             & \hspace{10mm} t = 0, i \in \mathcal{I} \label{eq:remaining1}\\
    %     % ret initialize
    %     & ret_{it} = ret\_ini_a
    %             & \hspace{10mm} t = 0, i \in \mathcal{I} \label{eq:remaining2}\\
    %     % fixed states during planning period
    %     & state_{ist} = 1
    %             & \hspace{10mm} t \in \mathcal{T}, i \in \mathcal{I}; s \in \mathcal{S}\, | if\, state\_ini_{it} = s \label{eq:fixedstates}
    % \end{align}

@@

\section{Conclusions and future work} 
    The present work proposes a new model for the Military Flight and Maintenance Problem. This formulation sets an interesting base for further model extensions in order to integrate more complex real constraints.

@@

\bibliographystyle{plain}
% \selectlanguage{english}
\bibliography{MFMP}
